Active Contextual Entropy Search

### 2016-06-14 2016_ICML/poster/defines/header.tex
Changes for final version of poster
Moving title down

\pgfdeclareimage[height=4.8cm]{dfki-logo}{./defines/DFKI_Schrift}

\setbeamertemplate{headline}
{%
  \setbeamercolor{mycolor}{fg=black,bg=white}
   \begin{beamercolorbox}{mycolor}
    \centering{\parbox{70cm}{\centering{\huge{\textbf{\inserttitle}}}}}\\[5mm]
    \centering{\parbox{70cm}{\centering{\Large{\insertauthor\\[.5cm] University Bremen,
Robotics Research Group, Robert-Hooke-Str.~1, 28359 Bremen,
Germany\hspace{2cm}}}}}

>>>>

\pgfdeclareimage[height=2.8cm]{dfki-logo}{./defines/Bosch-Logo.pdf}

\setbeamertemplate{headline}
{%
  \setbeamercolor{mycolor}{fg=black,bg=white}
   \begin{beamercolorbox}{mycolor}
    \raisebox{-1.5cm}{\centering{\parbox{70cm}{\centering{\huge{\textbf{\inserttitle}}}}}}

    \centering{\parbox{70cm}{\centering{\Large{\raisebox{-1.5cm}{\insertauthor}\\[.5cm] 
    University Bremen, Robotics Research Group, Robert-Hooke-Str.~1, 28359 Bremen, Germany\\
    Robert Bosch GmbH, Corporate Research CR/AEY2, 70442 Stuttgart, Germany}
}}}
